### 2025-09-06 machine-learning.qmd
20250906 - fix error due to renamed variables

nfl_actualStats_offense_weekly$player_id
nfl_expectedFantasyPoints_weekly$player_id

nfl_rankings$id

@@

nfl_expectedFantasyPoints_weekly <- nfl_expectedFantasyPoints_weekly %>% 
  mutate(
    season = as.integer(season),
    receptions = as.integer(receptions)) %>% 
  distinct(gsis_id, season, week, .keep_all = TRUE) # drop duplicated rows

>>>>

#nfl_actualStats_offense_weekly$player_id
nfl_expectedFantasyPoints_weekly$player_id

nfl_rankings_draft$id
nfl_rankings_weekly$fantasypros_id

@@

nfl_expectedFantasyPoints_weekly <- nfl_expectedFantasyPoints_weekly %>% 
  rename(gsis_id = player_id) %>% 
  mutate(
    season = as.integer(season),
    receptions = as.integer(receptions)) %>% 
  distinct(gsis_id, season, week, .keep_all = TRUE) # drop duplicated rows
